Breast Cancer Diagnosis Classification Analysis

### 2022-12-09 powerpoint.rmd

```{r}
# ggplot(train) +
#   geom_point(aes(x = concavity_mean, y = radius_mean, col = diagnosis))+
#   labs(x = "Concavity Mean", y = "Radius Mean", title = "Severity of Concavity vs. Radius of Tumor")
```

@@

## Model Assesments

>>>>

```{r}
ggplot(train) +
  geom_point(aes(x = concavity_mean, y = radius_mean, col = diagnosis))+
  labs(x = "Concavity Mean", y = "Radius Mean", title = "Severity of Concavity vs. Radius of Tumor")
```

@@

## Model Assessments
